%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.1 (8/1/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[letterpaper]{twentysecondcv} % a4paper for A4
\input{top.tex}
\begin{document}
\input{me.tex}

%----------------------------------------------------------------------------------------
%	 SKILLS
%----------------------------------------------------------------------------------------

% Skill bar section, each skill must have a value between 0 an 6 (float)
%\skills{{GIMP (Photoshop)/1.5/4}, {WinAPI/3.3/5},{Android/2.1/2},{Linux (Bash)/1.9/10},{JavaScript/2.8/5},{C\#/1.0/1},{C++/1.9/4},{Python/2.5/2},{Java/3.2/4},{C/5.6/10}}
\skills{{JQuery,Prototype.js/1.9},{XML/0.8},{CSS, LESS, Sass/2.8},{HTML/3.8},{MySQL/2.7},{C,C++,CGI/2.0},{Java, C\#/4.5},{JavaScript/3.7},{PHP/5.6}}


%----------------------------------------------------------------------------------------

\makeprofile % Print the sidebar

\input{education.tex}

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Web Experience}

\begin{twenty} % Environment for a list with descriptions

\twentyitem{2011-2022}{Home page}{ \href{https://dexp.in}{https://dexp.in} }{
\textit{Technologies:} Git, Jekyll, Sass, HTML5, CSS3, JavaScript.

{\small Source: \href{https://github.com/DeXP/dexp.github.io}{https://github.com/DeXP/dexp.github.io} }
}

	\twentyitem{2014-2015}{One Manga Day game}{ \href{https://onemangaday.dexp.in}{https://onemangaday.dexp.in} }{
\textit{Technologies:} Git, Jekyll, Sass, HTML5, CSS3, JavaScript.

{\small Site and game sources: \href{https://github.com/DeXP/onemangaday}{https://github.com/DeXP/onemangaday} }
}

	\twentyitem{2009-2012}{LiveMaster}{ \href{https://livemaster.ru}{https://livemaster.ru} }{
Role: PHP developer. I did both front-end and back-end. Implementation of help-system with administration/moderation interface. AJAX picture uploading with image crop. Prototype.js patch for local bugs. Pixel-perfect HTML and CSS layout. Written PHP and JavaScript code lines: $\sim$10k. \textit{Technologies:} PHP, MySQL, JavaScript, AJAX, Prototype.js, HTML, CSS, memcached.}

	\twentyitem{2005-2011}{Old personal website}{ \href{http://dexperix.net}{http://dexperix.net} }{
The engine is self-made, written in C++. Info stored in MySQL, with LaTeX-like syntaxis. \textit{Technologies:} C++, MySQL, LaTeX, HTML, CSS.
}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 OTHER INFORMATION
%----------------------------------------------------------------------------------------

\section{Other Experience}

\begin{twenty}

\twentyitem{2017-2022}{Enterprise Game Developer}{ \href{https://dexp.in/games}{https://dexp.in/games} }{
Employers: 2K Czech, Bohemia Interactive.

Games: Borderlands THC Ultra HD Texture Pack, Mafia: Definitive Edition, VIGOR.
}


\twentyitem{2014-2017}{Indie Game Developer}{ \href{https://store.steampowered.com/developer/dexp}{https://store.steampowered.com/developer/dexp} }{
Steam games: One Manga Day, Winter Novel, Wordlase.

Technologies: Python, C, RenPy, JSON, XML, gzip, PNG, OGG, libc, SDL, WinAPI, Linux, Mac OS X, steamworks.
}

\twentyitem{2012-2017}{Teacher at Gomel State Technical University}{ \href{https://www.gstu.by}{https://www.gstu.by} }{
Assistance in the following courses: Lisp, AI, Algorithmization, Object-oriented programming, Java, CAD-systems, Databases, Operation systems, Networks, Cloud computing.

Teaching at University's Android game development course.}

%\twentyitem{2012-2014}{Hardware developer}{ \href{https://www.gstu.by}{https://www.gstu.by} }{
%Working directly with flash memory, USB protocol, Pic8 controllers, STM ARM controllers, Xilinx FPGA. The same code worked on Linux, Windows and Pic-controller. Technologies: C, C++, VHDL, Qt.
%}
\end{twenty}
\input{links.tex}
\end{document} 
