%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.1 (8/1/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4
\input{top.tex}
\begin{document}
\input{me.tex}

%----------------------------------------------------------------------------------------
%	 SKILLS
%----------------------------------------------------------------------------------------

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills{%{GIMP (Photoshop)/1.5/4},
{WinAPI/3.3/5},{Android/2.1/2},{JavaScript/2.8/5},{C\#/5.1},{C++/1.9/4},{Python/2.5/2},{Java/3.2/4},{Linux/4.1/10},{C/5.6/10}}


%----------------------------------------------------------------------------------------

\makeprofile % Print the sidebar

\input{education.tex}

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Code samples / Tools}

\begin{twenty}
	\twentyitem{2017}{dxTarRead}{\href{https://dexp.in/tools/dxtarread/}{https://dexp.in/tools/dxtarread/}}{
A minimalistic non compressed archive file readers written in ANSI C. Supported formats: GNU tar, PAX, GNU ar, Cpio (4 variants).}

\twentyitem{2015}{dxPmdxConverter}{\href{https://github.com/DeXP/dxPmdxConverter}{https://github.com/DeXP/dxPmdxConverter}}{
Simple PMD/PMX to MQO/OBJ converter written in ANSI C. Console version exists for: Linux, Mac OS X, Windows; both 32 and 64 bit.}
\end{twenty}



\section{Open source contributions}

\begin{twenty}
	\twentyitem{2016-2017}{Nuklear}{\href{https://github.com/vurtun/nuklear/commits?author=DeXP}{https://github.com/vurtun/nuklear/commits?author=DeXP}}{
A single-header ANSI C gui library. My changes are mostly related to examples: adding new ones, adding new functionality to existent. 
%Some improvements: adding ability to load images to GDI+ and X11 backend, adding support of OpenGL ES 2.0 and Emscripten.

Used technologies: ansi C, OpenGL, OpenGL ES, SDL, GLFW, X11, GDI+, WinAPI, Emscripten, Linux, Windows, Raspberry Pi}

\twentyitem{2016}{Tiled}{\href{https://github.com/bjorn/tiled/pull/1357}{https://github.com/bjorn/tiled/pull/1357}}{
A generic tile map editor. I added an ability to convert property type. Used technologies: C++, Qt, Linux, Windows.}
\end{twenty}



\section{Game Development Experience}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2016-2017}{Wordlase}{\href{http://store.steampowered.com/app/602930}{http://store.steampowered.com/app/602930}}{
A word puzzle game, written in C. Game runs on Windows and Linux.

Used technologies: ansi C, libc, Nuklear, JSON, gzip, Python, SDL.

C code lines: $\sim$5k. Python code lines: $\sim$1k.

{\small Open source part - Nuklear+: \href{https://dexp.in/tools/nuklear-cross/}{https://dexp.in/tools/nuklear-cross/} }}


	\twentyitem{2015-2016}{Winter Novel}{\href{http://store.steampowered.com/app/485350}{http://store.steampowered.com/app/485350} }{
A visual novel ASCII game, written in low-level C. Windows, Linux.
		
A lot of functions were reimplemented. Used technologies: ansi C, no libc, WinAPI/SDL, OpenGL, Android. Strict Ansi C89.

Project size: $\sim$20k source code lines.}


%	\twentyitem{2014-2015}{One Manga Day}{\href{http://store.steampowered.com/app/365070}{http://store.steampowered.com/app/365070}}{
%A short visual novel originally written in Russian. The game is written in Python (RenPy engine). Music is self-made in Magix Music Maker. Graphics is made in Manga Maker Comipo.
%	
%{\small Source code: \href{https://github.com/DeXP/onemangaday}{https://github.com/DeXP/onemangaday}} }
\end{twenty}


\input{links.tex}
\end{document} 
