%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.1 (8/1/17)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4
\input{top.tex}
\begin{document}
\input{me.tex}

%----------------------------------------------------------------------------------------
%	 SKILLS
%----------------------------------------------------------------------------------------

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills{%{GIMP (Photoshop)/1.5/4},
{WinAPI/3.3/5},{Android/2.1/2},{Linux/4.1/10},{JavaScript/2.8/5},{C\#/1.0/1},{C++/1.9/4},{Python/2.5/2},{Java/3.2/4},{C/5.6/10}}


%----------------------------------------------------------------------------------------

\makeprofile % Print the sidebar

\input{education.tex}

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Game Development Experience}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2016-2017}{Wordlase}{\href{http://store.steampowered.com/app/602930}{http://store.steampowered.com/app/602930}}{
A word puzzle game, written in C.

Used technologies: ansi C, libc, Nuklear, JSON, gzip, Python, SDL.

C code lines: $\sim$5k. Python code lines: $\sim$1k.}


	\twentyitem{2015-2016}{Winter Novel}{\href{http://store.steampowered.com/app/485350}{http://store.steampowered.com/app/485350} }{
A visual novel ASCII game, written in low-level C. 
		
A lot of functions were reimplemented. ``printf'' for example (to have colors on all platforms). Used technologies: ansi C, no libc, WinAPI/SDL, OpenGL, Android. Strict Ansi C89.

Project size: $\sim$20k source code lines.}


	\twentyitem{2014-2015}{One Manga Day}{\href{http://store.steampowered.com/app/365070}{http://store.steampowered.com/app/365070}}{
A short visual novel originally written in Russian. The game is written in Python (RenPy engine). Music is self-made in Magix Music Maker. Graphics is made in Manga Maker Comipo.
	
{\small Source code: \href{https://github.com/DeXP/onemangaday}{https://github.com/DeXP/onemangaday}} }
\end{twenty}

%----------------------------------------------------------------------------------------
%	 OTHER INFORMATION
%----------------------------------------------------------------------------------------

\section{Other Experience}

%\subsection{Review}

%Alice approaches Wonderland as an anthropologist, but maintains a strong sense of noblesse oblige that comes with her class status. She has confidence in her social position, education, and the Victorian virtue of good manners. Alice has a feeling of entitlement, particularly when comparing herself to Mabel, whom she declares has a ``poky little house," and no toys. Additionally, she flaunts her limited information base with anyone who will listen and becomes increasingly obsessed with the importance of good manners as she deals with the rude creatures of Wonderland. Alice maintains a superior attitude and behaves with solicitous indulgence toward those she believes are less privileged.

\begin{twenty}
\twentyitem{2012-2017}{Teacher at Gomel State Technical University}{ \href{https://www.gstu.by}{https://www.gstu.by} }{
Assistance in the following courses: Lisp, AI, Algorithmization, Object-oriented programming, Java, CAD-systems, Databases, Operation systems, Networks, Cloud computing.

Teaching at University's Android game development course.}

\twentyitem{2012-2014}{Hardware developer}{ \href{https://www.gstu.by}{https://www.gstu.by} }{
Working directly with flash memory, USB protocol, Pic8 controllers, STM ARM controllers, Xilinx FPGA. The same code worked on Linux, Windows and Pic-controller. Technologies: C, C++, VHDL, Qt.
}

\twentyitem{2009-2012}{PHP developer}{ \href{https://www.livemaster.ru}{https://www.livemaster.ru} }{
Both front-end and back-end. Implementation of help-system with AJAX administration/moderation interface. 
Technologies: PHP, MySQL, JavaScript, AJAX, HTML, CSS, memcached, Linux.
}

\end{twenty}
\input{links.tex}
\end{document} 
